### 2012-12-18 MSWL_ECO_lesson2.tex
fixes #4: Revision: Impact on stakeholders and markets, strategic aspects

\chapter{Impact on stakeholders and markets, strategic aspects}

@@

The debate at class started with different approaches, some were inclined to the GPL because it ensured the continuity of the project under the same trend, others by Apache because commercial companies in general have less resistance to such licenses, and others ultimately could not come to any conclusion. Eventually all converged to that there is no formula with calculated results, the choice of a FLOSS license type usually depends on at least the following premises:

@@

\section{Impact on companies using software and in the production fabric}

One thing is very clear when talking about the economic impact that a business strategy can produce, and it is to be focused from a purely practical point of view. In this sence we watched the video\footnote{http://www.parc.com/event/1092/open-for-business.html} of a lecture at PARC (Palo Alto Research Center) about \textquotedblleft Open for business: Building successful commerce around open source", whose presenter was M\aa rten Mickos, Eucalyptus Systems CEO and ex-CEO of MySQL AB, two successful OSS companies.\\

Some main ideas about the presentation are:

@@

\section{The Economic Motivation of Open Source Software: Stakeholder Perspectives}\label{Part II}

@@

Based on the fact that the hardware is usually maintained at a stable price, by reducing the costs associated with licensing fees when using FLOSS software, integrators can vary as desired, whether the services provided or the price associated with such services. This represents a great advantage over the use of proprietary software, in the sense that profits areas are more flexible, that is, starting from a certain cost, theoretically can be increased the number of services offered, or could be decreased the price of services in order to attract more customers.\\

@@

\section{Conclusions}\label{conclusions}

In working process... by Daniel G\'amez.\\

>>>>

\chapter{Impact on stakeholders and markets, strategic aspects}\label{Chapter 2}

@@

The debate at class started with different approaches, some were inclined to the GPL because it ensures the continuity of the project under the same trend, others by Apache because commercial companies in general have less resistance to such licenses, and others ultimately could not come to any conclusion. Eventually all converged to that there is no formula with calculated results, the choice of a FLOSS license type usually depends on at least the following premises:

@@

\section{Impact on companies using software and in the production fabric}\label{Section 2.1}

One thing is very clear when talking about the economic impact that a business strategy can produce, and it is to be focused from a purely practical point of view. In this sence we watched the video\footnote{http://www.parc.com/event/1092/open-for-business.html} of a lecture at PARC (Palo Alto Research Center) about \textquotedblleft Open for business: Building successful commerce around open source", whose presenter was M\aa rten Mickos, Eucalyptus Systems CEO and ex-CEO of MySQL AB, two successful OSS companies. Some main ideas about the presentation are:

@@

\section{The Economic Motivation of Open Source Software: Stakeholder Perspectives}\label{Section 2.2}

@@

Based on the fact that the hardware is usually maintained at a stable price, by reducing the costs associated with licensing fees when using FLOSS integrators can vary as desired, whether the services provided or the price associated with such services. This represents a great advantage over the use of proprietary software, in the sense that profits areas are more flexible, that is, starting from a certain cost, theoretically can be increased the number of services offered, or could be decreased the price of services in order to attract more customers.\\

\pagebreak

@@

\section{Conclusions}\label{Conclusions Chapter 2}

Making a general analysis we can see that through FLOSS there is a viable business option, ways to compete in the market and new business opportunities. It is important to make a preliminary assessment of the business to determine whether or not the FLOSS fits on it. In many cases FLOSS is the most efficient, but not always, anyway FLOSS is highly adaptable and conformance to needs, it will always provide an alternative to which pay attention at.\\

It has been said also that this is a service economy, bringing software as a service, instead of software as a product. This changes traditional rules and allows opportunities for new stakeholders on certain fields, with the premise of innovate to get real competitiveness on the market.\\

The benefits provided by the FLOSS are endless, but it is necessary to understand them, understand their environment, assume the appropriate role, be innovative and make the best of it, as in any business strategy.
